Similar 'win-stay, lose-switch' tendencies have been found in other motor learning studies \cite{taylor_flexible_2011}. The finding of 'win-stay, lose-switch' in our study suggests that elite sportspeople seek effective strategies. One plausible explanation for not finding corroborating evidence for group differences in choice or on 'win-stay, lose-switch' is that we were dealing with highly experienced coaches with solid sports knowledge. Therefore, we should be cautious in describing this as a null result. It is also important to note that coaches had access to skiers' race times and underwent significant learning too. In a typical training situation, coaches might not have tested strategies as extensively as in this study.  






differs from acquiring skills at an acceptable level in that it requires years of extensive and high-quality training. Such training improves performance in two key ways: first, by honing precision in action execution, a process that occurs incrementally and slowly. Second, the training can modify the strategies selected to solve the task that can lead to larger leaps in performance if the selected strategies are effective. Despite the crucial role that cognitive strategies play in overcoming plateaus and facilitating continuous skill improvement, our understanding of how these strategies are acquired, as well as our insights into which teaching methods are effective for learning this specific skill component, remain limited. If superior methods to those currently used in standard practice exist, they could prove invaluable for training both present and future generations of learners.




We found that reinforcement learning improved race times more during the acquisition phase and performed better during retention than supervised (free-choice) learning. Both treatment groups chose better strategies during the sessions, with a clear 'win-stay, lose-switch' signature showing that they tended to stick to successful strategies. Despite the descriptively greater tendency for reinforcement learning to select better strategies and to have more pronounced "win-stay, lose-switch" tendencies during acquisition, these differences were not significantly different, nor were their contrasts at any of the sessions. However, we found that reinforcement learning had lower costs for suboptimally chosen strategies, indicating that the skiers had acquired a better cognitive understanding of the strategies' effect. However, this explanation does not comprehensively account for the disparity in race time. Compared with supervised (free choice) learning, reinforcement learning achieved greater improvement in the 'extend' strategy, suggesting that reinforcement feedback might have increased motor motivation. However, the reinforcement learning group did not outperform the supervised (target skill) learning group. This speaks to the importance of learning strategies. Interestingly, despite their clear difference in race time, the supervised (target skill) learning group did not significantly differ between the 'extend' and 'rock skis forward' strategies, suggesting the benefits of exposing learners to various strategies. Overall, we suggest that coaches can enhance skill learning by developing strategies and allowing learners to gain insights into their causal effects from evaluations instead of pure instruction.



A surprising finding was that the predicted probability of choosing the estimated best strategy decreased from free choice 2 to retention for reinforcement learning. At the same time, it increased for the supervised (free choice) learning group, leading to a significant interaction effect. This difference in change resulted in supervised learning (free choice) actually having a marginally higher predicted probability of choosing the estimated best strategy, contrary to our hypothesis. Nevertheless, we found that reinforcement learning skied better in retention and incurred lower costs (measured as regret) from their supoptimal chosen strategies compared to supervised (free choice) learning. One interpretation of this result is that skiers also took into account the risk associated with the execution of strategies, opting for those with lower risk. In that case, one might consider that "extend with rock skis forward" could be more exposed to risk since it could potentially make athletes lean to far backward to make the next turn.  However, this does not seem to be the case, as observed from both Figure 5a and the raw data in Figure 4, where the choices of this strategy have increased. Therefore, it appears that, at least on average, this is not a good account of our data. A more likely one is that that the skiers in reinforcement learning better grasped the effects of the different strategies and learned that some strategies were equally effective so that it did not matter much which they chose.

Our data can also be explained in a neuroeconomic framework \cite{pietro_mazzoni_why_2007, dudman_basal_2016}  by reinforcement learning increasing motor vigor. Executing repetitive up-and-down movements down a slalom course using the 'extend' and 'extend with rock skis forward' strategies is more energy expensive than performing the 'stand against' or 'rock skis forward' strategies. Besides having the energy to choose these strategies, it is possible that reinforcement learning had higher motor vigor when performing these strategies. That is, they performed the strategies with more power and quicker execution, which generally translates into better performance in ski racing given the snow resists the forces without being compressed. Previous studies on vigor have found that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster towards targets paired with rewards than unpaired targets. It is therefore possible that the reinforcement learning increased motor vigor. Comments from several coaches, who watched the retention and transfer, from the sideline, was that the skiers in the reinforcement learning group tended to use more arm movements than skiers in the other groups, despite the instruction did not tell them to do that. The vigor perspective may also help explaining why reinforcement learning did not learn better than the supervised (target skill) learning group, as previous studies also have found that training with explicit knowledge boosts motor vigor much like the effect of reward itself \cite{anderson_rewards_2020, wong_explicit_2015}. It may therefore be that the getting information that one strategy was best from a current World Cup coach may have boosted the implicit motivation to perform this strategy well. 



, suggesting that strategy selection may have played an important role in learning. Interestingly, the supervised (target skill) learning group struggled to differentiate between the 'extend' and 'rock skis forward' strategies despite their clear race time difference, suggesting the benefits of exposing learners to various strategies. Exposing learners to different strategies might therefore be beneficial. Taken collectively, we suggest that coaches can enhance skill learning by developing strategies within their sport and allowing athletes to evaluate them, rather than always instructing learners.

Retention...

Our hypothesis was that reinforcement learning improves transfer to a new slalom course. The rationale for such expected behaviour was that reinforcement learning would achieve better insights into to the strategies' effect, thereby promoting better decision-making in new situations. However, we found no corroborating evidence for this hypothesis. This result aligns with studies that have observed enhanced retention but not transfer with reinforcement compared to supervised learning \cite{hasson_reinforcement_2015}. Furthermore, reinforcement learning has been found to yield a lower generalization signature in adaptive tasks \cite{lior_shmuelof_overcoming_2012}. One account for these findings is that reinforcement learning improves learning only for the specific situations in which one has been rewarded, as these are the instances in which learning has been reinforced. A potential mechanism for this is that training with rewards shortens the time window during which memory is unstable, affecting learners' capacity to extend learning to new situations \cite{robertson_memory_2018}. It is also conceivable that a more structured learning approach, where learners are exposed to frequent switches between strategies, is necessary to grasp the task's structure and promote transfer \cite{braun_structure_2010}. Future research should possibly investigate the effect of structural learning. 



Our study suggests that reinforcement learning can be an essential training strategy to improve skill acquisition. However, before encouraging coaches and instructors to implement this strategy, we discuss the significance of the effect size and its amplifying and counteracting mechanisms for generalizability \cite{anvari_not_2023}. To start this discussion, we emphasize that the estimated effect size during retention was smaller than our predefined smallest effect size of interest. This benchmark, however, was set for a longer slalom course and more training sessions than we could execute due to space and time constraints in the ski hall. Consequently, we exercise caution in outright dismissing its practical significance. Instead, we aim to help the reader understand its potential importance for skill improvement in our sample of skiers. The first step towards this insight is to consider that the slalom course approximately equaled one-third of a full slalom race course, and a slalom race consists of two runs. Therefore, the 0.12 seconds effect size could be scaled up by a factor of 6, potentially proving significant for coaches in a more accurate course setup. However, racecourses consisting solely of flat sections are rare, and it is more realistic to assume that a flat section of a course constitutes only one-third of the entire course. If we base our understanding on this assumption, we can convert the 0.12-second difference into FIS world ranking positions. Considering that a race consists of two runs, this translates into an improved World Rank of 27 positions for females and 65 for males, based on a median ranking of 600 in our sample (see Supplement discussion). This could be of significant importance, but we have to remember that this effect cannot be directly transferred, as sports expertise also involves cognitive decisions \cite{mangalam_investigating_2023, krakauer_motor_2019}, such as switching from one strategy to another during a race. Our study did not capture such decisions as we focused on flat sections. In conclusion, the estimated effect could be larger if not because reinforcement learning and supervised learning conducted the retention and transfer tests simultaneously. This design choice allowed the skiers to observe each other, possibly diluting some of the effect. However, this decision was made to mirror the conditions of alpine competitions and gave us confidence that athletes experienced similar conditions during testing. 

Our initial explanation for the improved acquisition and retention in the reinforcement learning group was that they learned to choose better strategies through evaluation via choice. During acquisition, we found that reinforcement learning enhanced its choices, while we did not observe the same evidence for supervised (free choice) learning. Both groups exhibited a 'win-stay, lose-switch' signature, indicating a tendency to stick to successful strategies. Despite reinforcement learning showing a descriptive tendency to select better strategies and having more pronounced "win-stay, lose-switch" tendencies during acquisition, these differences were not statistically significant, contrary to our initial hypothesis. 



Through their opportunity to evaluate the strategies adopted during acquisition, it appears that the skiers in reinforcement learning had discovered that they could choose among several strategies that had approximately similar effects. This approach reduced their risk of choosing a strategy with poor expected outcomes. This account cannot fully explain the group differences in race time, however. Reinforcement learning also improved upon the 'extend' strategy over the course of the sessions. Given that this group was not assigned a coach to help them improve, it is likely that the reinforcement feedback increased motor vigor when performing that surgery. Indeed, previous studies have shown that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster toward targets paired with rewards than unpaired targets.


Despite no convincing evidence that reinforcement learning selected the best strategy more often compared to supervised (free choice) learning, they had a lower expected cost (or regret) for their suboptimal chosen strategies during retention. Through their opportunity to evaluate the strategies during acquisition, it appears that the skiers in the reinforcement learning had discovered that they could choose among several strategies that gave approximately similar effects. This reduced their risk of grossly choosing a strategy with poor expected outcome. This account cannot fully explain the group differences in race time, however. Reinforcement learning also had greater improvement on the 'extend' strategy over the course of the sessions. As this group was not assigned a coach to help them improve, it is likely that the reinforcement feedback increased motor vigor when performing that startegy.  Indeed, previous studies have found that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster towards targets paired with rewards than unpaired targets. 




, suggesting that reinforcement feedback might have increasing motor vigor \cite{pietro_mazzoni_why_2007, dudman_basal_2016}, such that their "energized" this action better. Indeed, previous studies have found that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster towards targets paired with rewards than unpaired targets. 





to eller flere strategier ga tilnærmet lik effekt og valgte 



utøverne bedre klarte å skille mellom strategiene. 



Although we did not find evidence that reinforcement learning selected the best strategy more often compared to supervised (free choice) learning, they had a lower expected cost of their suboptimal choices during retention. Through evaluating,  the skiers in the reinforcement learning group may have acquired a better understanding of strategys' effects, thereby giving them better conditions to avoid very bad choices.


we observed that the expected cost of suboptimal choices was significantly lower in reinforcement learning compared to supervised (free choice) learning. 

 


Selv om vi ikke fant evidens for at reinforcement learning valgte bedre direkte på den beste strategien fant vi at den forventede kostnaden av å velge suboptimalt var langt lavere i reinforcement learning enn i supervised (free choice) learning. Ved å evaluere strategiene via tidene kan utøverne i reinforcement learning gruppen ha utviklet en bedre forståelse for strategienes effekter, og dermed unngått å bomme veldig ved deres suboptimale valg. 


lært gjennom evaluering ved å se tidene kan utøverne ha utviklet en bedre forståelse for strategiene, og dermed unngått å bomme veldig ved deres suboptimale valg. Dette perspektivet samsvarer med at forskjellen på 'strekk' og 'strekk og skyv' var liten og kanskje vanskelig å skille for utøveren i reinforcement learning gruppen. Dermed utgjorde det liten forskjell å velge den ene eller den andre. 

This explanation, however, cannot fully account for the disparity in race time. Compared with supervised (free choice) learning, reinforcement learning achieved greater improvement in the 'extend' strategy, suggesting that reinforcement feedback might have increasing motor vigor \cite{pietro_mazzoni_why_2007, dudman_basal_2016}, such that their "energized" this action better. Indeed, previous studies have found that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster towards targets paired with rewards than unpaired targets. Comments from a few coaches, who watched the retention and transfer, from the sideline, uttered that skiers in the reinforcement learning group used more forceful arm movements than skiers in the other groups, despite the instruction did not tell them to do that.





A surprising finding was that supervised (free choice) learning had a descriptively higher predicted probability of choosing the skier's estimated best strategy on retention. Still, the reinforcement learning had the fastest race times during retention. One interpretation of this result is that skiers in the reinforcement learning group took into consideration the variability of performing a strategy and opted for those with lower incurred risk \cite{braun_risk-sensitivity_2011, wolpert_motor_2010}, despite another strategy being more effective. This understanding may have arisen because skiers in the reinforcement learning group discovered that multiple strategies led to similar outcomes and chose the slightly worse strategy due to lower variability. In that case, one might consider that "extend with rock skis forward" to be more risky since it could potentially make athletes lean too far backward to be able to engage the skis in the next turn. However, this does not seem to be a good account of our data as the choices of this strategy increased on retention. A more likely explanation is that that the skiers in reinforcement learning built a better mental representation of the strategies and learned that two or more produced the same outcomes, and just picked any of them.

This explanation, however, cannot fully account for the disparity in race time. Compared with supervised (free choice) learning, reinforcement learning achieved greater improvement in the 'extend' strategy, suggesting that reinforcement feedback might have increasing motor vigor \cite{pietro_mazzoni_why_2007, dudman_basal_2016}, such that their "energized" this action better. Indeed, previous studies have found that people make saccades \cite{takikawa_modulation_2002} and reach\cite{summerside_vigor_2018} faster towards targets paired with rewards than unpaired targets. Comments from a few coaches, who watched the retention and transfer, from the sideline, uttered that skiers in the reinforcement learning group used more forceful arm movements than skiers in the other groups, despite the instruction did not tell them to do that.

The vigor perspective may also help explaining why reinforcement learning did not learn better than the supervised (target skill) learning group, as previous studies also have found that training with explicit knowledge boosts motor vigor much like the effect of reward itself \cite{anderson_rewards_2020, wong_explicit_2015}. It may therefore be that the getting information from a current World Cup coach that one strategy was best boosted the implicit motivation to perform this strategy well. 

